Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-12 paper/paper.Rmd
participants

This study aimed to answer two key questions around the presentation of spatial distributions:

1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?

2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?

Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.

The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis:

@@

The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.

@@

We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.

Participants were able to choose to participate by selecting this task from the list of tasks available to them.
Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website. 
There were 95 participants involved in the study. All of these participants read the introductory materials and viewed example questions before proceeding to the survey. Each participant was trained using three test displays orienting them to the evaluation task.
All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.

>>>>

This study aims to answer two key questions around the presentation of spatial distributions:

1. Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
2. Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?

Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.

<!--
The mean of the detection rate for choropleth map, denoted as $\mu_C$, and the hexagon tile maps, $\mu_H$ will be contrasted. This leads to the following one sided hypothesis:

@@

The detection rate $\hat\pi$ is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.
-->

@@

Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website. There were 95 participants involved in the study. All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task. All participants who completed the task were compensated $USD5 for their time, via the Figure-Eight payment system.

### 2020-01-12 paper/paper.tex
participants

This study aimed to answer two key questions around the presentation of spatial distributions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map display?
\item
  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map display?
\end{enumerate}

Additional considerations when completing this experimental task included exploration of the difficulty experienced by participants and the certainty they felt about their decision.

The mean of the detection rate for choropleth map, denoted as \(\mu_C\), and the hexagon tile maps, \(\mu_H\) will be contrasted. This leads to the following one sided hypothesis:

\(H_0\) : \(\mu_H\) = \(\mu_C\)
\(H_a\) : \(\mu_H\) \textgreater{} \(\mu_C\)

The detection rate \(\hat\pi\) is calculated as the amount of people that made the choice of plot that contained the real data, out of the participants who saw data plot in the lineup of the null data plots.

@@

We recruited participants for the survey style task to test the effectiveness of the hexagon tile map display.
The lineup protocol expects that the participants are uninvolved judges that had no prior knowledge of the data to avoid discrimination or advantages.
The Figure-Eight crowd source platform was used to advertise the survey to potential participants that had achieved level 2 or level 3 on the Figure-Eight Platform.
The participants were chosen as they have experience with survey tasks that involve evaluating images. The participants were at least 18 years old, as it is a requirement of the platform.

Participants were able to choose to participate by selecting this task from the list of tasks available to them.
Participants were allocated to either group A or group B when they proceeded to the survey web application, hosted externally from the Figure-Eight website.
There were 95 participants involved in the study. All of these participants read the introductory materials and viewed example questions before proceeding to the survey. Each participant was trained using three test displays orienting them to the evaluation task.
All participants who volunteered to take part were compensated for their time via the payment system of Figure-Eight.

>>>>

This study aims to answer two key questions around the presentation of spatial distributions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Are spatial disease trends that impact highly populated small areas detected with higher accuracy, when viewed in a hexagon tile map?
\item
  Are people faster in detecting spatial disease trends that impact highly populated small areas when using a hexagon tile map?
\end{enumerate}

Additional considerations when completing this experimental task included the difficulty experienced by participants and the certainty they had in their decision.

@@

Participants were recruited for to evaluate lineups from the Figure-Eight crowdsourcing platform (XXX REF).
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

Participants were allocated to either group A or group B when they proceeded to the survey web application, which was hosted externally to the Figure-Eight website. There were 95 participants involved in the study. All participants read introductory materials, and was trained using three test displays, to orient them to the evaluation task. All participants who completed the task were compensated \$USD5 for their time, via the Figure-Eight payment system.
